---
title: "Coronoa Virus Data Set"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Column Description
Main file in this dataset is covid_19_data.csv and the detailed descriptions are below.

covid_19_data.csv

Sno - Serial number
ObservationDate - Date of the observation in MM/DD/YYYY
Province/State - Province or state of the observation (Could be empty when missing)
Country/Region - Country of observation
Last Update - Time in UTC at which the row is updated for the given province or country. (Not standardised and so please clean before using it)
Confirmed - Cumulative number of confirmed cases till that date
Deaths - Cumulative number of of deaths till that date
Recovered - Cumulative number of recovered cases till that date

2019_ncov_data.csv

This is older file and is not being updated now. Please use the covid_19_data.csv file

Added two new files with individual level information

COVID_open_line_list_data.csv
This file is obtained from this link

COVID19_line_list_data.csv
This files is obtained from this link

Country level datasets
If you are interested in knowing country level data, please refer to the following Kaggle datasets:
South Korea - https://www.kaggle.com/kimjihoo/coronavirusdataset
Italy - https://www.kaggle.com/sudalairajkumar/covid19-in-italy

```{r}
library('ggplot2')
library('lubridate')
library('dplyr')
library('gridExtra')
```

```{r}
df <- read.csv(file = './data/covid_19_data.csv')
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
unique(df$Country.Region)
summary(df)
```
```{r}

df
df2 <- df %>% group_by(ObservationDate,Country.Region) %>% summarise(Confirmed = sum(Confirmed),
                                                                     Deaths = sum(Deaths),
                                                                     Recovered = sum(Recovered))

```
```{r}

confirmed = ggplot(df2,aes(x=ObservationDate,y = Confirmed, color = Country.Region) ) + geom_line() + theme(legend.position = "none") 
deaths = ggplot(df2,aes(x=ObservationDate,y = Deaths, color = Country.Region) ) + geom_line() + theme(legend.position = "none") 
recovered = ggplot(df2,aes(x=ObservationDate,y = Recovered, color = Country.Region) ) + geom_line() + theme(legend.position = "none") 
grid.arrange(confirmed, deaths,recovered, nrow = 1)

```
